Universal Anonymous Signatures

### 2022-05-13 prism-backend/research/gsac/app-building-blocks.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.
Quick full pass (excl. appendices).

\subsection{An Instantiation of \SBCM with BBS+}

@@

\subsubsection{Security.} Next, we sketch that the given BBS+ interactive
signing protocol is correct, OMF-secure, and ensures blindness.

\paragraph{Correctness.} \todo{XXX}

\paragraph{OMF security.} The proof for OMF security is essentially the
same as that of EUF security for BBS+ signatures \cite{cdl16b}, which gives a
reduction against the $q$-SDH problem. There is only one exception: in the proof
for BBS+ EUF-security, when the adversary against EUF-security queries a
signature, the simulator (the adversary against $q$-SDH) has to simulate the
signature. For this, it requires the $l$ messages in the message set to be
signed, which in plain BBS+ it is not a problem, as they are received in the
clear. In the case of \SBCM, however, some of the messages to be signed are
received as part of a commitment. Note however that, in \SBCM, besides receiving
the commitment, we also receive a NIZK proof of knowledge of the corresponding
messages. Thus, the adversary against $q$-SDH in the OMF case only needs to
extract the witnesses from the proof. This is doable after soundness of NIZK.
If the NIZK also has online-extractability, then we do not need to impose
further requirements. If it is not, then the \SBCM scheme should not allow
parallel signing requests, or limit the total number of signatures to be
created to a logarithmic function of the security parameter (which is probably
not reasonable in most cases; although it may be for group signature-like
settings). We refer to \cite[Lemma 1]{cdl16b} for the full details of the proof
of EUF security in BBS+.
%
\todo{If needed, do the actual proof. Should essentially be a copy-paste of
  that in \cite{cdl16b}...}

>>>>

\subsubsection{An Instantiation of \SBCM with BBS+}

@@

\paragraph{Correctness.} Correctness is direct from correctness of the
commitment scheme, the NIZK system, and BBS+.

\paragraph{OMF security.} The proof for OMF security is essentially the
same as that of EUF security for BBS+ signatures \cite{cdl16b}, which gives a
reduction against the $q$-SDH problem. There is only one exception: in the proof
for BBS+ EUF-security, when the adversary against EUF-security queries a
signature, the simulator (the adversary against $q$-SDH) has to simulate the
signature. For this, it requires the $l$ messages in the message set to be
signed, which in plain BBS+ it is not a problem, as they are received in the
clear. In the case of \SBCM, however, some of the messages to be signed are
received as part of a commitment. Note however that, in \SBCM, besides receiving
the commitment, we also receive a NIZK proof of knowledge of the corresponding
messages. Thus, the adversary against $q$-SDH in the OMF case only needs to
extract the witnesses from the proof. This is doable after soundness of NIZK.
If the NIZK also has online-extractability, then we do not need to impose
further requirements. If it is not, then the \SBCM scheme should not allow
parallel signing requests, or limit the total number of signatures to be
created to a logarithmic function of the security parameter (which is probably
not reasonable in most cases; although it may be for group signature-like
settings). We refer to \cite[Lemma 1]{cdl16b} for the full details of the proof
of EUF security in BBS+.
%
\jdv{If needed, do the actual proof. Should essentially be a copy-paste of
  that in \cite{cdl16b}...}

### 2022-05-13 prism-backend/research/gsac/conclusion.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.
Quick full pass (excl. appendices).

Even though the generalization effort we do is significant, there are still
ways to go further.
%
For instance, we do not hide the issuer(s) of the
credential(s) employed to produce a signature (resp., request a new credential).
Thus, we can only ensure privacy among signatures (resp., credential requests)
that involve credentials issued by the same issuer set. While hiding the issuers
of the involved credentials is certainly possible (we show how to do it at
signing time, in order to build ring signatures), we argue that it may be
desirable to leave it as is, at least, initially. The reason being that issuers
are still what conveys trust to a system where credentials contain attributes
attested by these issuers. Indeed, if it is already hard for verifiers to decide
whether or not to trust an unanonymous issuer, one can imagine that it would be
even harder to decide whether or not to trust an anonymous one. This question
is core to the domain of trust registries \needcite, for instance.
%
A second desirable improvement, perhaps clearer from a technical point of view,
is to extend our model to support non-trivial utility and accountability across
multiple signatures from the same signer. More concretely, let our \feval and
\finsp functions (and perhaps also \fissue?) operate on multiple signatures by
the same \usk. That can lead to an extended \UAS scheme which would support
advanced use cases such as rate limiting (or $k$-TAA \cite{asm06}); or might
be even privately training an AI model based on one's authenticated
past activity, and prove that the model has been trained honestly.

>>>>

Even though the generalization effort we do is significant, there are still
ways to go further.
%
For instance, we do not hide the issuer(s) of the
credential(s) employed to produce a signature (resp., request a new credential).
Thus, we can only ensure privacy among signatures (resp., credential requests)
that involve credentials issued by the same issuer set. While hiding the issuers
of the involved credentials is certainly possible (we show how to do it at
signing time, in order to build ring signatures), we argue that it may be
desirable to leave it as is, at least, initially. The reason being that issuers
are still what conveys trust to a system where credentials contain attributes
attested by these issuers. Indeed, if it is already hard for verifiers to decide
whether or not to trust a non-anonymous issuer, one can imagine that it would be
even harder to decide whether or not to trust an anonymous one. This question
is core to the domain of trust registries, for instance.
%
A second desirable improvement, perhaps clearer from a technical point of view,
is to extend our model to support non-trivial utility and accountability across
multiple signatures from the same signer. More concretely, let our \feval and
\finsp functions (and perhaps also \fissue?) operate on multiple signatures by
the same \usk. That can lead to an extended \UAS scheme which would support
advanced use cases such as rate limiting (or $k$-TAA \cite{asm06}); or might
be even privately training an AI model based on one's authenticated
past activity, and prove that the model has been trained honestly.

### 2022-05-13 prism-backend/research/gsac/construction-uas.tex
Fixed error in unfor-sign property and proof.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.
Quick full pass (excl. appendices).

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. In \todo{\secref{sec:instantiation}}, we give a concrete
instantiation.

We use three different NP relations in our generic construction. Namely:

\begin{description}
\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs the rules for issuing
  new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
  (\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
  \CCommit(usk) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
  Basically, this relation requires that, in order to issue a credential with
  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
  prove knowledge of it, as well as prove that all additional credentials needed
  for the issuing to be granted, meet some defined policy \fissue.
\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
  verifiers define them. Governs what utility information is directly revealed
  by signatures. It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
  \attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec =
  \EEnc(\Eek,\yinsp;r) \land \yeval = \feval(\usk,\scred,\msg) \land
  \yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$, with
  $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
  nutshell, this relation ensures that signatures will produce the correct
  signature evaluation and opening values, and that any credential used to
  create the signature is bound to the same \usk key.
\item[$\NIZKRel_{\Open}$:] Set by openers, governs the utility information
  to be extracted by the \Open algorithm. It is defined as $\NIZKRel_{\Open} =
  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$. It proves
  that the decryption of the opening utility value has been done correctly.
\end{description}

@@

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
To generate its key pair, each opener first parses \parm as $(\cdot,\cdot,
\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
(\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
(\Ssk,\finsp)$, $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk \gets
(\Ssk,\Edk)$. Finally, returns $(\opk,\osk)$.

\paragraph{$\usk \gets \UKeyGen(\parm)$.} %
Each user, prior to requesting credentials, generates his secret key by parsing
\parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\AttrSpace)$, and picking randomly
$\usk \getr \AttrSpace$. Finally, return \usk.

>>>>

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. We use three different NP relations in our generic
construction. Namely:

\begin{description}
\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs via \fissue the rules for
  issuing new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
  \CCommit(usk;r) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
  Basically, this relation requires that, in order to issue a credential with
  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
  prove knowledge of it, as well as prove that all additional credentials needed
  for the issuing to be granted, meet some defined policy \fissue.
\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
  verifiers define them. Governs via \feval and \finsp what utility
  information is directly revealed by signatures, or extracted by openers.
  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
  \attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec =
  \EEnc(\Eek,\yinsp;r) \land \yeval = \feval(\usk,\scred,\msg) \land
  \yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$, with
  $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
  nutshell, this relation ensures that signatures will produce the correct
  signature evaluation and opening values, and that any credential used to
  create the signature is bound to the same \usk key.
\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
\end{description}

@@

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
To generate its key pair, each opener first parses \parm as $(\cdot,\cdot,
\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
(\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
(\Ssk,\finsp)$, $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk \gets
(\Ssk,\Edk)$.

\paragraph{$\usk \gets \UKeyGen(\parm)$.} %
Each user, prior to requesting credentials, generates his secret key by parsing
\parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\AttrSpace)$, and picking randomly
$\usk \getr \AttrSpace$.

### 2022-05-13 prism-backend/research/gsac/introduction.tex
Quick full pass (excl. appendices).

% What is the context for this research? Introduce previous works on this topic,
% in one paragraph. (Privacy-preserving identities, with accountability (APPI))
Successful identity representation, management, and usage are, on its own, among
the toughest problems in the Internet and digital communications at large%
\footnote{``Digital identity is one of the 21st century's biggest challenges'':
  \href{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}. Last access, May 12th, 2022.}.
Just as an illustration, think
of usernames and passwords, which end up being unmanageable as soon as we need
to start remembering a few%
\footnote{``The problem of passwords and how to deal with it'': \url{https://www.computerweekly.com/feature/The-problem-of-passwords-and-how-to-deal-with-it}. Last access,
May 12th, 2022.}; or traditional vertical PKIs, like X.509 \cite{rfc5280},
which are too rigid, and frequently require too much trust; or
horizontal PKIs, such as PGP, that are also too rigid, and are hard to manage
and scale\footnote{``What's the matter with PGP?'': \url{https://blog.cryptographyengineering.com/2014/08/13/whats-matter-with-pgp/}. Last access, May 12th, 2022}.
If, in addition, we require privacy, the scenario becomes even more
challenging. Technologies like OpenID\footnote{\url{https://openid.net/}. Last
  access, May 12th, 2022.} and OAuth\footnote{\url{https://oauth.net/}. Last
  access, May 12th, 2022.} make identity more
manageable (from the point of view of service providers) through Single Sign
On solutions. But this comes at the cost of introducing centralization points
that gain way too much knowledge beyond what is actually necessary. Holding
users accountable, or extracting utility out of their actions, is trivial in
this cases -- although that comes at the cost of barely having privacy.

@@

Concerning (2), it is even surprising that, during the almost 30 years of
research in group signatures, the notion of ``identity'' of a group member
mostly reduces to an integer representing the order in which a user joined
the group -- or, at the most, some long-term public key. Thus, even with
notorious efforts to generalize accountability in group signatures,
re-identifying the signer from an index still forces to assume an external
ecosystem that endows that index with actual real world identyfing information.
Needless to say, this introduces further points of centralization, and
trust assumptions.

@@

In this work, we make our attempt on addressing both questions. We start with a
direct combination of GS and AC. While this does not pose many definitional nor
technical challenges, it is a good exercise to showcase benefits obtained from
even a simple combination. This directly answers in the affirmative our first
question above. However, a direct combination does not address at all the
flexibility that we aim at -- simply because it inherits the limitations of
the vanilla GS and AC approaches we build on. Thus, we make an extra step with
the goal to add such flexibility, spanning three diretions, allowing:

@@

In fact, taking this unifying path is a low hanging fruit if one looks at recent
works. For instance, BBS+ signatures \cite{asm06,cdl16b} have been used recently
to build both group signatures \cite{gl19,dl21,fgl21}, but are also one of the
main candidates to incorporate anonymity into verifiable credentials%
\footnote{``W3C Credential Exchange using BBS+ Signatures'',
  \url{https://github.com/hyperledger/aries-rfcs/blob/main/features/0646-bbs-credentials/README.md}. Last access May 11th, 2020.}.%
The interest of the verifiable credentials community in BBS+ is not accidental,
though, as BBS+ follow the CL signatures line of work \cite{cl02}. CL signatures
allow creating a single signature over a set of messages, which can be directly
used to bundle a set of attributes (messages) into the same signature
(credential). Indeed, this was the trigger for some of the first, and possibly
the most fruitful branch of, anonymous credentials systems (see
\cite{cl01,cl02,cl04}, among others). Other very closely related signature
scheme, PS16 \cite{ps16} can
also be used to build group signatures, see \cite[Appendix A.1]{ps15} or
\cite{cdl+20}; as well as anonymous credentials \cite[Appendix A.2]{ps15} or
\cite{sms+19}.

@@

Additionally, within the AC domain, some works allow proving arbitrary claims
over the attributes in a credential \cite{bcc+09,cklm14,dmm+18,fhs19}; while
others simply allow to
selectively disclose subsets of these attributes. For \GSAC, we do the latter.
Despite not being the most general option (although it is more general than the
GS approach, as it does not even have attributes), it is enough to illustrate
the advantages of unifying both worlds. Again, in \UAS we generalize this
aspect.

Finally, modelling-wise we also have two choices: follow a UC-based definition
\cite{cane20}, or a game-based one \cite{shoup04}. Independently on the pros and
cons of each, in GS the standard is the game-based approach
\cite{bmw03,bsz05,bcc+16,kty04,ky05}, although close relatives to GS, like DAA,
prefer the UC approach \cite{cdl16,cdl16b,ccd+17,cdl17}. On the AC line of work,
while some UC models exist \cite{}, game-based definitions also seem prevalent
\cite{bcc+09,cks10,cl11,cklm12,cmz14,dmm+18,fhs19}.
Thus, the logical choice (at least, for a first step) seems to be game-based
definitions. Concretely, we take strong inspiration from \cite{bsz05} for the
GS branch, and from \cite{fhs19} for the AC one.

\subsubsection{\UAS: Generalizing \GSAC.} %
\GSAC is the first step towards achieving identity and authentication systems
with both utility and accountability, yet it presents some limitations. Some we
have already mentioned: it models a system with only one issuer, only allows
using one credential to produce a signature, and only supports selective
disclosure. We overview other limitations, that we address also with \UAS.

@@

\paragraph{Generalizing signature generation.} %
Another generalization point is on the utility revealed at signing time. As
stated, in \GSAC we restrict to selective disclosure. This is already a
generalization with respect to GS, where this is not considered, possibly with
the only exception of \cite{khad07a,khad07b,emo09,aa14}. These works on
Attribute-Based Group Signatures (ABGS) are however too restricive:
\cite{khad07a,khad07b,aa14} only consider fixed rules to apply over an
attribute set in order to be able to create signatures (i.e., if a different
ruleset is to be applied, a new group is needed). \cite{emo09} allows some
alterations to previous rules, but instead require updates of the group public
key, which is probably unacceptable in most situations. Instead of following the
ABGS approach, we adopt the AC one, and simply require that the signer has to
prove some arbitrary claim over the attributes in the credentials s/he uses to
create a signature. This is thus orthogonal to group/issuer public key
generation, which is what forces ABGS to update them every time a change in the
rules takes place. Our approach to allow revealing arbitrary utility information
at signing time is to let signers/verifiers decide on a \emph{signature
  evaluation function}, \feval, which operates on the user secret key, the
user credentials, and the signed message. This \feval function thus defines what
verifiers (or third parties) will learn straight away from a valid signature.
Note though that signing does not only reduce to simply computing (and proving)
\feval's output. In addition, users have to prove that all the employed
credentials are bound to the same user key, and that the opening information
(more on this next) is also correct. This means that it is perfectly valid to
define \feval functions that reveal absolutely nothing (e.g., always output
$0$), and yet have a meaningful signing operation. Modelling-wise, this forces
us to restrict that, in the anonymity property, the produced challenge
signatures must produce the same \feval output, which may seem too strong,
although it seems hard to avoid. The only alternative we find is actually a
useful generalization, which is to formulate anonymity with a simulation-based
approach. While still compatible with cases in which the output of \feval has
the same in both challenge signatures, it additionally allows useful
constructions in which the output of \feval is encrypted, e.g., under the
opener's key. In this way, only the opener will learn it, when/if needed -- it
removes utility at signing time, but gives more flexibility at opening time,
without sacrificing privacy.

>>>>

% What is the context for this research? Introduce previous works on this topic,
% in one paragraph. (Privacy-preserving identities, with accountability (APPI))
Successful identity representation, management, and usage are, on its own, among
the toughest problems in the Internet and digital communications at large%
\footnote{``Digital identity is one of the 21st century's biggest challenges'':
  \href{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}. Last access, May 12th, 2022.}.
Just as an illustration, think
of usernames and passwords, which end up being unmanageable as soon as we need
to start remembering a few%
\footnote{``The problem of passwords and how to deal with it'': \url{https://www.computerweekly.com/feature/The-problem-of-passwords-and-how-to-deal-with-it}. Last access,
May 12th, 2022.}; or traditional vertical PKIs, like X.509 \cite{rfc5280},
which are too rigid, and frequently require too much trust; or
horizontal PKIs, such as PGP, that are also too rigid, and are hard to manage
and scale\footnote{``What's the matter with PGP?'': \url{https://blog.cryptographyengineering.com/2014/08/13/whats-matter-with-pgp/}. Last access, May 12th, 2022}.
If, in addition, we require privacy, the scenario becomes even more
challenging. Technologies like OpenID\footnote{\url{https://openid.net/}. Last
  access, May 12th, 2022.} and OAuth\footnote{\url{https://oauth.net/}. Last
  access, May 12th, 2022.} make identity more
manageable (from the point of view of service providers) through Single Sign
On solutions. But this comes at the cost of introducing centralization points
that gain way too much knowledge beyond what is actually necessary. Holding
users accountable, or extracting utility out of their actions, is trivial in
these cases -- although that comes at the cost of barely having privacy.

@@

Concerning (2), it is even surprising that, during the roughly 30 years of
research in group signatures, the notion of ``identity'' of a group member
mostly reduces to an integer representing the order in which a user joined
the group -- or, at the most, some long-term public key. Thus, even with
notorious efforts to generalize accountability in group signatures,
re-identifying the signer from an index still forces to assume an external
ecosystem that endows that index with actual real world identyfing information.
Needless to say, this introduces further points of centralization, and
trust assumptions.

@@

In this work, we make our attempt on addressing both questions. We start with a
direct combination of GS and AC. While this does not pose many definitional nor
technical challenges, it is a good exercise to showcase benefits obtained from
even a simple combination. This directly answers in the affirmative our first
question above. However, a direct combination does not achieve at all the
flexibility that we aim at -- simply because it inherits the limitations of
the vanilla GS and AC approaches we build on. Thus, we make an extra step with
the goal to add such flexibility, spanning three diretions, allowing:

@@

In fact, taking this unifying path is a low hanging fruit if one looks at recent
works. For instance, BBS+ signatures \cite{asm06,cdl16b} have been used recently
to build both group signatures \cite{gl19,dl21,fgl21}, but are also one of the
main candidates to incorporate anonymity into verifiable credentials%
\footnote{``W3C Credential Exchange using BBS+ Signatures'',
  \url{https://github.com/hyperledger/aries-rfcs/blob/main/features/0646-bbs-credentials/README.md}. Last access May 11th, 2020.}.%
The interest of the verifiable credentials community in BBS+ is not accidental,
though, as BBS+ follows the CL signatures line of work \cite{cl02}. CL signatures
allow creating a single signature over a set of messages, which can be directly
used to bundle a set of attributes (messages) into the same signature
(credential). Indeed, this was the trigger for some of the first, and possibly
the most fruitful branch of, anonymous credentials systems (see
\cite{cl01,cl02,cl04}, among others). Other very closely related signature
scheme, PS16 \cite{ps16} can
also be used to build group signatures, see \cite[Appendix A.1]{ps15} or
\cite{cdl+20}; as well as anonymous credentials \cite[Appendix A.2]{ps15} or
\cite{sms+19}.

@@

Additionally, within the AC domain, some works allow proving arbitrary claims
over the attributes in a credential \cite{bcc+09,cklm14,dmm+18,fhs19}; while
others simply allow to selectively disclose subsets of these attributes
\cite{cks10,cl11,cdhk15,hs21}. For \GSAC, we do the latter.
Despite not being the most general option (although it is more general than the
GS approach, as it does not even have attributes), it is enough to illustrate
the advantages of unifying both worlds. Again, in \UAS we generalize this
aspect.

Finally, modelling-wise we also have two choices: follow a UC-based definition
\cite{cane20}, or a game-based one \cite{shoup04}. Independently on the pros and
cons of each, in GS the standard is the game-based approach
\cite{bmw03,bsz05,bcc+16,kty04,ky05}, although close relatives to GS, like DAA,
prefer the UC approach \cite{cdl16,cdl16b,ccd+17,cdl17}. On the AC line of work,
while some UC models exist \cite{cks10}, game-based definitions also seem
prevalent \cite{bcc+09,cl11,cklm12,cmz14,dmm+18,fhs19}.
Thus, the logical choice (at least, for a first step) seems to be game-based
definitions. Concretely, we take strong inspiration from \cite{bsz05} for the
GS branch, and from \cite{fhs19} for the AC one.

\subsubsection{\UAS: Generalizing \GSAC.} %
\GSAC is the first step towards achieving privacy-preserving identity and
authentication systems with both utility and accountability, yet it presents
some limitations. Some we have already mentioned: it models a system with only
one issuer, only allows using one credential to produce a signature, and only
supports selective disclosure. We overview other limitations, that we address
also with \UAS.

@@

\paragraph{Generalizing signature generation.} %
Another generalization point is on the utility revealed at signing time. As
stated, in \GSAC we restrict to selective disclosure. This is already a
generalization with respect to GS, where this is not considered, possibly with
the only exception of \cite{khad07a,khad07b,emo09,aa14}. These works on
Attribute-Based Group Signatures (ABGS) are however too restricive:
\cite{khad07a,khad07b,aa14} only consider fixed rules to apply over an
attribute set in order to be able to create signatures (i.e., if a different
ruleset is to be applied, a new group is needed). \cite{emo09} allows some
alterations to previous rules, but instead require updates of the group public
key, which is probably unacceptable in most situations. Instead of following the
ABGS approach, we adopt the AC one, and simply require that the signer has to
prove some arbitrary claim over the attributes in the credentials s/he uses to
create a signature. This is thus orthogonal to group/issuer public key
generation, which is what forces ABGS to update them every time a change in the
rules takes place. Our approach to allow revealing arbitrary utility information
at signing time is to let signers/verifiers decide on a \emph{signature
  evaluation function}, \feval, which operates on the user secret key, the
user credentials, and the signed message. This \feval function thus defines what
verifiers (or third parties) will learn straight away from a valid signature.
Note though that signing does not only reduce to simply computing (and proving)
\feval's output. In addition, users have to prove that all the employed
credentials are bound to the same user key, and that the opening information
(more on this next) is also correct. This means that it is perfectly valid to
define \feval functions that reveal absolutely nothing (e.g., always output
$0$), and yet have a meaningful signing operation. Modelling-wise, this forces
us to restrict that, in the anonymity property, the produced challenge
signatures must produce the same \feval output, which may seem too strong,
although it seems hard to avoid. The only alternative we find is actually a
useful generalization, which is to formulate anonymity with a simulation-based
approach. While still compatible with cases in which the output of \feval has
the same value in both challenge signatures, it additionally allows useful
constructions in which the output of \feval is encrypted, e.g., under the
opener's key. In this way, only the opener will learn it, when/if needed -- it
removes utility at signing time, but gives more flexibility at opening time,
without sacrificing privacy.
